A Recipe for Scavenging - the natural history of a behaviour

### 2016-04-28 natural history of scavenging.tex
Minor edits

\subsection*{Metabolism}
Because of the sporadic nature of carrion we would expect adaptations that reduce energetic costs of maintenance to be selected for in scavengers as it would allow for longer inter-feeding periods. 
Extant reptiles possess an advantage here, in that over the course of a year their food requirements can be 30 times lower than an endotherm of equal size \citep{Nagy1621}.
\cite{devault2002scavenging} suggest this is an avenue for scavenging in snakes because they ``exhibit exceedingly low maintenance metabolisms, and most can survive on a few scant feedings per year.
It is, therefore, possible for snakes to rely largely on infrequent, less energy-rich meals."
In the same review the authors found occurrences of scavenging spread across five families of snakes and stated that this behaviour is ``far more common than currently acknowledged."\citep{devault2002scavenging}.
The same reasoning can be applied to crocodiles and their allies \citep{forrest2003evidence,moleon2015carcass}. 
\cite{carey1982temperature} found ectothermic sharks have the ability to go weeks between meals because they focus on the energy-rich sections of carcasses (see Handling Time). 
Endotherms have also evolved physiological mechanisms that allow them to depress their otherwise high metabolic rates at certain times e.g. vultures who do so while resting at their roost and during periods of food deprivation \citep{bahat1998nocturnal}.

@@

The groups from which these modern soaring birds arose, appear during the Palaeocene \citep[66 - 56 Million years ago (Mya); ][]{Jetz2012, Jarvis2014} and Cretaceous \citep{chiappe2006early} respectively. 
However, soaring flight is likely to be far older than this with avian flight originating in the Late Jurassic (163.5-145 Mya) and vertebrate flight in the Late Triassic (235-201.3 Mya) coincident with the pterosaurs. 
Indeed, scavenging among pterosaurs has been hypothesised many times before \citep{witton2008reappraisal}. 
Certain groups of these animals could reach enormous sizes \citep[e.g. Azhdarchids with wingspans of 11 metres; ][]{witton2010size} and, notably, appear to have engaged in soaring flight \citep{witton2010size}.
It seems probable that at least some of these extinct species used soaring as a means for scavenging \citep{witton2013pterosaurs}. 
%KH added "at least some of these" as it was not clear what species used soaring as a means for scavenging.
While soaring is perhaps the only viable means of locomotion that allows for an obligate, scavenging life-style \citep{ruxton2004obligate}, powered flight is still an efficient means of locomotion. 
Certainly, avian flight is cheaper than either walking or running \citep{tucker1975energetic}.

@@

Sharks are one likely candidate for general scavenging behaviors as their locomotion, which depends on large pectoral fins to generate lift as they swim, resembles that of the large soaring fliers.
Many shark species have large foraging ranges \citep[e.g. the great white sharks \textit{Carcharodon carcharias};][]{bruce2006movements} and it seems reasonable that they would use oceanographic currents to further reduce movement costs \citep{ruxton2004energetic}.
In fact, facultative scavenging is seen in many selachian groups, including species of extant sharks like white sharks \citep[known to feed on whale carcasses;][]{fallows2013white}, Greenland sharks \citep[feeding on seals;][]{watanabe2012slowest}, and sixgill sharks \citep{anderson2016impact}. 
There is evidence too of scavenging in extinct species, where shark teeth have been found in the remains of dinosaurs, mosasaurs and Pliocene mysticete whales \citep[5.3-3.6 Mya; ][]{schwimmer1997scavenging,ehret2009caught}.

Interestingly, style of swimming in fish does not significantly affect the cost of movement \citep{williams1999evolution}, hence it is likely that many aquatic species with large ranges will encounter scavenging opportunities. 
It is perhaps jaw morphology that is more likely to define which species can avail of carcasses.
%KH I moved this down here as it kinda throws our shark soaring thing out the window (which I like as a linking function). However I think this kinda solves our problems in the complexity of swimming by saying apart from large ranges ability to eat is probably more important.

We might expect then that by combining an aquatic environment and an endothermic metabolism marine mammals would especially prosper as scavengers. %, especially as this group has perhaps the largest home range of any animals (whales and shit).
Fossil pinnipeds and cetaceans from 60 Mya have transitional features indicative of their evolutionary trajectory to fully aquatic species \citep{williams1999evolution}.  
But despite their movement away from land their energetic savings were negligible because the \textit{total} cost incurred by a swimming marine mammal is high \citep{williams1999evolution}. 
Indeed, the total energetic cost is similar to an equivalent terrestrial or aerial mammal \citep{williams1999evolution}.
This underscores the trade offs between the benefits of endothermy in terms of activity periods and the costs of maintaining such an energetically expensive system. 
That said, aquatic endotherms have and do scavenge. 
For instance, early whales such as \textit{Basilosaurus} (38-36.5 Mya) seem to have fit into the same niche as killer whales (\textit{Orcinus orca}) and we have some evidence for scavenging in both \citep{fahlke2012bite,Whitehead415}.

@@

%% AK:  Need to be careful here because this whole idea of sprawling posture being worse off than erect posture is not that well supported in the literature. 
%% Great Transformations in Vertebrate Evolution By Kenneth P. Dial, Neil Shubin, Elizabeth L. Brainerd talks about it at length 
%% So I think this should stay pitched as an endo/ ectothermy thing rather than posture 
Terrestrial environments are the most energetically costly in which to move \citep{tucker1975energetic}. 
Unlike aerial and aquatic environments support must be provided through the animal's posture. % leading to trade offs between low cost of maintain and the efficiency of transport. 
The early transition from a sprawling gait, seen in early tetrapods, to the more erect posture of synapsids and later dinosaurs and mammals, has often been supposed as conferring a huge advantage to the latter groups \citep{sullivan2015posture}.
The purported advantages include benefits in terms of speed, efficiency, muscle effort and manoeuvrability \citep{sullivan2015posture}.
Clearly, for a scavenger, an ability to efficiently cover an area at a high speed would increase the encounter rate with carrion. 
Despite being intuitive, \cite{sullivan2015posture} states most of the hypotheses in favour of this idea remain to be tested in the context of archosaur evolution. 
One noted consequence of a sprawling gait is the phenomenon known as Carrier's constraint such that the animal can't move and undergo costal ventilation at the same time because the lateral movements impedes its lungs \citep{carrier1987evolution}. 
The evolution of an upright posture has been offered as one of the primary mechanisms that allowed early archosaurs to overcome this constraint \citep{uriona2008recruitment}.

@@

% Although the earliest evidence of vertebrate scavenging comes from the Permian (298.9 - 252.17 Mya) where a temnospondyl amphibian fed on the carcass of \textit{Varanops}, a predatory synapsid of the time \citep{reisz2006articulated}. 
Whatever the case, it is with the evolution of endothermy in the therapsid-mammal lineage \citep{clarke2010temperature} that terrestrial vertebrates would have gained the ability to range more widely, a vital component in seeking out carrion.
Modern endothermic mammals can sustain longer periods of energetically expensive activity \citep{bennett1979endothermy} resulting in larger foraging ranges. 
Today, terrestrial scavenging in the mammals is probably best known in an African context where hyenas, jackals and lions all take sizeable proportions of carrion in their diet.
In the spotted hyena (\textit{Crocuta crocuta}), striped hyena (\textit{Hyaena hyaena}) and brown hyena (\textit{Hyaena brunnea}) it can be over 90\% \citep{jones2015african}.
And although no contemporary terrestrial vertebrate exists as an obligate scavenger, most, if not all, are facultative to some extent \citep{beasley2015vertebrates}.
The particular reliance of hyenas on carrion means we can use them as examples of efficient terrestrial scavengers to compare with other forms. 
In terms of locomotion, they employ a characteristic ``rocking horse gait"  which allows them to cover great distances efficiently, loping at 10 km/hr \citep{mills1989comparative,jones2015african}. 
Such long-distance travel is apparent in African wild dogs (\textit{Lycaon pictus}) and many other canids \citep{pennycuick1995radius,janis2014forelimb}. 
In contrast, big cats like leopards (\textit{Panthera pardus}) rely on ambush \citep{pennycuick1995radius}. 
This allows us to make a broad distinction between the ambush strategies of cat-like forms and the pursuit/ pounce strategies of more dog-like forms, the latter being more suited to scavenging \citep{janis2014forelimb}. 
These insights allow us to compare extant terrestrial species to their prehistoric forebears given the dominance of mammalian carnviores since the Eocene (56-33.9 Mya) where the order split into the Caniforma and Feliforma \citep{van1987skeletal}.
To take one example, \cite{anyonge1996locomotor} found that \textit{Nimravides}, a genus of sabretooth cat from the Miocence (10.3 to 5.3 Mya), were likely to have been ambush predators which would argue against them taking a lot of carrion.

@@

Staying in the aquatic setting, the phenomenon of occasional bounties of carrion in the form of whale falls has led some researchers to investigate if an obligate scavenger could survive by seeking out these remains exclusively.
\cite{ruxton2005searching} argued that although this is energetically feasible it's ecologically unlikely.
Any animal that could find such whale carcasses is unlikely to have ignored other types of carrion.
Although no aquatic species have ever exceeded the size of whales, some enormous animals have evolved in this environment before the evolution of cetaceans, including \textit{Leedsichthys}, a bony fish from the Middle Jurassic (174.1-163.5 Mya) and the aquatic Mesozoic reptiles, the plesiosaurs, pliosaurs and ichtyosaurs, that could all exceed 15 metres in length \citep{ruxton2011zoology,danise2014ecological}.

@@

\section*{Handling Time}
Since the food a scavenger depends upon is not dispatched directly, often the most easily accessible and choicest components of the carcass will be missing owing to the activity of predators and other scavengers, or, if present, will be subject to decay as well as competition.
So being able to overcome competitors and maximise the nutrient gain from the remnants are all essential parts of carcass handling time.

@@

Again, we can draw a comparison with clades that are lacking in these features. 
As we mentioned earlier the skull morphology of extinct sabretooths meant they would have left a large amount of flesh on a carcass and were unable to feed on bones \citep{palmqvist2011giant}. 
Extant bats are also poorly equipped when it comes to feeding on carrion; the larger forms are typically frugivores and therefore lack the adaptations for digesting meat, while the smaller carnivorous bats are mainly found in the microbats, which are insectivorous \citep{aguirre2003implications}.   
That said, Necromantis (“death-eater”), a large bat from the middle to late Eocene (56-33.9 Mya) had a robust cranio-mandibular morphology, and is a likely candidate for an extinct scavenging bat \citep{Weithofer_Necromantis_1887,Hand_Necromantis_2012}.

@@

\begin{figure}[!htbp]
\centering
   \includegraphics[width=1\textwidth]{timeline_figure/timeLine.pdf}
\caption{The diversity of scavengers through time. Each species has either direct evidence for it being a scavenger or would be positioned high up on our scavenging scale. The three lines represent the three different environments (from top to bottom: aerial, terrestrial and aquatic). Time is represented on the horizontal axis with each third representing respectively the Paleozoic (541 to 252 Mya), the Mesozoic (252 to 66 Mya) and the Cenozoic (66 Mya to the present).}
%Silhouettes from left to right in each different environment: Aerial: \textit{Some pterosaur}, Azhdarchid (which one?), Diomedeidae, \textit{Gyps}, \textit{Some preybird}; Terrestrial: \textit{Some mammaliaform?}, \textit{Some temnospondyl?}, \textit{Allosaurus}?, \textit{Dilophosaurus}?, \textit{Canis lupus?}, \textit{Crocuta crocuta}, \textit{Some shneakyshnake}, \textit{Homo sapiens}; Aquatic: \textit{Tiktaalik}, \textit{Some antiarchplacoderm}, Ichtyosauridae, \textit{Some metriorhynchidae?}, Mosasauridae, \textit{Basilosaurus}, \textit{Carcharodon carcharias}, \textit{Orcinus orca}.
\label{Timeline}
\end{figure}

\section*{Conclusion} 
As is often the case in science, the present provides the key to the past.
The animals of today, while often different (sometimes radically so) to their ancestors, can be used to make informed comparisons to extinct species. 
We have used this technique to give insight into the drivers of scavenging across vertebrates through time.
In common with any other forager be they grazer, browser or predator, scavengers past and present have had to balance their energetic costs with the gains of food. 
The main factors we considered namely, encounter rate, handling time and prey availability can be used to create a scale of scavenging whereupon any species can be placed in order to establish the importance of carrion in it diet.
We hope this approach will be useful in the effort to explore this most understudied of feeding ecologies. 
% Add bits on climate change/dectection rate change, etc...

>>>>

\subsection*{Metabolism}
Because of the sporadic nature of carrion we would expect adaptations that reduce energetic costs of maintenance to be selected for in scavengers as it would allow for longer inter-feeding periods. 
Extant reptiles possess an advantage here, in that over the course of a year their food requirements can be 30 times lower than an endotherm of equal size \citep{Nagy1621}.
\cite{devault2002scavenging} suggest this is an avenue for scavenging in snakes because they ``exhibit exceedingly low maintenance metabolisms, and most can survive on a few scant feedings per year.
It is, therefore, possible for snakes to rely largely on infrequent, less energy-rich meals."
In the same review the authors found occurrences of scavenging spread across five families of snakes and stated that this behaviour is ``far more common than currently acknowledged."\citep{devault2002scavenging}.
The same reasoning can be applied to crocodiles and their allies \citep{forrest2003evidence,moleon2015carcass}. 
\cite{carey1982temperature} found that sharks, as ectothermics, have the ability to go weeks between meals because they focus on the energy-rich sections of carcasses (see Handling Time \ref{handlingTime}). 
Endotherms have also evolved physiological mechanisms that allow them to depress their otherwise high metabolic rates at certain times e.g. vultures who do so while resting at their roost and during periods of food deprivation \citep{bahat1998nocturnal}.

@@

The groups from which these modern soaring birds arose, appear during the Palaeocene \citep[66 - 56 Million years ago (Mya); ][]{Jetz2012, Jarvis2014} and Cretaceous \citep{chiappe2006early} respectively. 
However, soaring flight is likely to be far older than this with avian flight originating in the Late Jurassic (163.5 - 145 Mya) and vertebrate flight in the Late Triassic (235 - 201.3 Mya) coincident with the pterosaurs. 
Indeed, scavenging among pterosaurs has been hypothesised many times before \citep{witton2008reappraisal}. 
Certain groups of these animals could reach enormous sizes \citep[e.g. Azhdarchids with wingspans of 11 metres; ][]{witton2010size} and, notably, appear to have engaged in soaring flight \citep{witton2010size}.
It seems probable that at least some of these extinct species used soaring as a means for scavenging \citep{witton2013pterosaurs}. 
%KH added "at least some of these" as it was not clear what species used soaring as a means for scavenging.
While soaring is perhaps the only viable means of locomotion that allows for an obligate, scavenging life-style \citep{ruxton2004obligate}, powered flight is still an efficient means of locomotion. 
Certainly, avian flight is cheaper than either walking or running \citep{tucker1975energetic}.

@@

Sharks are one likely candidate for general scavenging behaviors as their locomotion, which depends on large pectoral fins to generate lift as they swim, resembles that of the large soaring fliers.
Many shark species have large foraging ranges \citep[e.g. the great white sharks \textit{Carcharodon carcharias};][]{bruce2006movements} and it seems reasonable that they would use oceanographic currents to further reduce movement costs \citep{ruxton2004energetic}.
In fact, facultative scavenging is seen in many selachian groups, including species of extant sharks like white sharks \citep[known to feed on whale carcasses;][]{fallows2013white}, Greenland sharks \citep[feeding on seals;][]{watanabe2012slowest}, and sixgill sharks \citep{anderson2016impact}. 
There is evidence too of scavenging in extinct species, where shark teeth have been found in the remains of dinosaurs, mosasaurs and Pliocene mysticete whales \citep[5.3 - 3.6 Mya; ][]{schwimmer1997scavenging,ehret2009caught}.

Interestingly, however, style of swimming in fishes does not significantly affect the cost of movement \citep{williams1999evolution}, hence it is likely that many aquatic species with large ranges will encounter scavenging opportunities. 
It is perhaps jaw morphology that is more likely to define which species can avail of carcasses.
%KH I moved this down here as it kinda throws our shark soaring thing out the window (which I like as a linking function). However I think this kinda solves our problems in the complexity of swimming by saying apart from large ranges ability to eat is probably more important.

We might expect then that by combining an aquatic environment and an endothermic metabolism marine mammals would especially prosper as scavengers. %, especially as this group has perhaps the largest home range of any animals (whales and shit).
Fossil pinnipeds and cetaceans from 60 Mya have transitional features indicative of their evolutionary trajectory to fully aquatic species \citep{williams1999evolution}.  
But despite their movement away from land their energetic savings were negligible because the \textit{total} cost incurred by a swimming marine mammal is high \citep{williams1999evolution}. 
Indeed, the total energetic cost is similar to an equivalent terrestrial or aerial mammal \citep{williams1999evolution}.
This underscores the trade offs between the benefits of endothermy in terms of activity periods and the costs of maintaining such an energetically expensive system. 
That said, aquatic endotherms have and do scavenge. 
For instance, early whales such as \textit{Basilosaurus} (38 - 36.5 Mya) seem to have fit into the same niche as killer whales (\textit{Orcinus orca}) and we have some evidence for scavenging in both \citep{fahlke2012bite,Whitehead415}.

@@

%% AK:  Need to be careful here because this whole idea of sprawling posture being worse off than erect posture is not that well supported in the literature. 
%% Great Transformations in Vertebrate Evolution By Kenneth P. Dial, Neil Shubin, Elizabeth L. Brainerd talks about it at length 
%% So I think this should stay pitched as an endo/ ectothermy thing rather than posture 
Terrestrial environments are the most energetically costly in which to move \citep{tucker1975energetic}. 
Unlike aerial and aquatic environments support must be provided through the animal's posture. % leading to trade offs between low cost of maintain and the efficiency of transport. 
The early transition from a sprawling gait, seen in early tetrapods, to the more erect posture of synapsids and later dinosaurs and mammals, has often been supposed as conferring a huge advantage to the latter groups \citep{sullivan2015posture}.
The purported advantages include benefits in terms of speed, efficiency, muscle effort and manoeuvrability \citep{sullivan2015posture}.
Clearly, for a scavenger, an ability to efficiently cover an area at a high speed would increase the encounter rate with carrion. 
Despite being intuitive, \cite{sullivan2015posture} states most of the hypotheses in favour of this idea remain to be tested in the context of archosaur evolution. 
One noted consequence of a sprawling gait is the phenomenon known as Carrier's constraint such that the animal can't move and undergo coastal ventilation at the same time because the lateral movements impedes its lungs \citep{carrier1987evolution}. 
The evolution of an upright posture has been offered as one of the primary mechanisms that allowed early archosaurs to overcome this constraint \citep{uriona2008recruitment}.

@@

% Although the earliest evidence of vertebrate scavenging comes from the Permian (298.9 - 252.17 Mya) where a temnospondyl amphibian fed on the carcass of \textit{Varanops}, a predatory synapsid of the time \citep{reisz2006articulated}. 
Whatever the case, it is with the evolution of endothermy in the therapsid-mammal lineage \citep{clarke2010temperature} that terrestrial vertebrates would have gained the ability to range more widely, a vital component in seeking out carrion.
Modern endothermic mammals can sustain longer periods of energetically expensive activity \citep{bennett1979endothermy} resulting in larger foraging ranges. 
Today, terrestrial scavenging in the mammals is probably best known in an African context where hyenas, jackals and lions all take sizeable proportions of carrion in their diet.
In the spotted hyena (\textit{Crocuta crocuta}), striped hyena (\textit{Hyaena hyaena}) and brown hyena (\textit{Hyaena brunnea}) it can be over 90\% \citep{jones2015african}.
And although no contemporary terrestrial vertebrate exists as an obligate scavenger, most, if not all, are facultative to some extent \citep{beasley2015vertebrates}.
The particular reliance of hyenas on carrion means we can use them as examples of efficient terrestrial scavengers to compare with other forms. 
In terms of locomotion, they employ a characteristic ``rocking horse gait"  which allows them to cover great distances efficiently, loping at 10 km/hr \citep{mills1989comparative,jones2015african}. 
Such long-distance travel is apparent in African wild dogs (\textit{Lycaon pictus}) and many other canids \citep{pennycuick1995radius,janis2014forelimb}. 
In contrast, big cats like leopards (\textit{Panthera pardus}) rely on ambush \citep{pennycuick1995radius}. 
This allows us to make a broad distinction between the ambush strategies of cat-like forms and the pursuit/ pounce strategies of more dog-like forms, the latter being more suited to scavenging \citep{janis2014forelimb}. 
These insights allow us to compare extant terrestrial species to their prehistoric forebears given the dominance of mammalian carnviores since the Eocene (56-33.9 Mya) where the order split into the Caniforma and Feliforma \citep{van1987skeletal}.
To take one example, \cite{anyonge1996locomotor} found that \textit{Nimravides}, a genus of sabretooth cat from the Miocence (10.3 - 5.3 Mya), were likely to have been ambush predators which would argue against them taking a lot of carrion.

@@

Staying in the aquatic setting, the phenomenon of occasional bounties of carrion in the form of whale falls has led some researchers to investigate if an obligate scavenger could survive by seeking out these remains exclusively.
\cite{ruxton2005searching} argued that although this is energetically feasible it's ecologically unlikely.
Any animal that could find such whale carcasses is unlikely to have ignored other types of carrion.
Although no aquatic species have ever exceeded the size of whales, some enormous animals have evolved in this environment before the evolution of cetaceans, including \textit{Leedsichthys}, a bony fish from the Middle Jurassic (174.1 - 163.5 Mya) and the aquatic Mesozoic reptiles, the plesiosaurs, pliosaurs and ichtyosaurs, that could all exceed 15 metres in length \citep{ruxton2011zoology,danise2014ecological}.

@@

\section*{Handling Time}
\label{handlingTime}
Since the food a scavenger depends upon is not dispatched directly, often the most easily accessible and choicest components of the carcass will be missing owing to the activity of predators and other scavengers, or, if present, will be subject to decay as well as competition.
So being able to overcome competitors and maximise the nutrient gain from the remnants are all essential parts of carcass handling time.

@@

Again, we can draw a comparison with clades that are lacking in these features. 
As we mentioned earlier the skull morphology of extinct sabretooths meant they would have left a large amount of flesh on a carcass and were unable to feed on bones \citep{palmqvist2011giant}. 
Extant bats are also poorly equipped when it comes to feeding on carrion; the larger forms are typically frugivores and therefore lack the adaptations for digesting meat, while the smaller carnivorous bats are mainly found in the microbats, which are insectivorous \citep{aguirre2003implications}.   
That said, Necromantis (“death-eater”), a large bat from the middle to late Eocene (56 - 33.9 Mya) had a robust cranio-mandibular morphology, and is a likely candidate for an extinct scavenging bat \citep{Weithofer_Necromantis_1887,Hand_Necromantis_2012}.

@@

\begin{figure}[!htbp]
\centering
   \includegraphics[width=1\textwidth]{timeline_figure/timeLine.pdf}
\caption{The diversity of scavengers through time. Each species has either direct evidence for it being a scavenger or would be positioned high up on our scavenging scale. The three lines represent the three different environments (from top to bottom: aerial, terrestrial and aquatic). Time is represented on the horizontal axis with each third representing respectively the Paleozoic (541 - 252 Mya), the Mesozoic (252 - 66 Mya) and the Cenozoic (66 Mya to the present).}
%Silhouettes from left to right in each different environment: Aerial: \textit{Some pterosaur}, Azhdarchid (which one?), Diomedeidae, \textit{Gyps}, \textit{Some preybird}; Terrestrial: \textit{Some mammaliaform?}, \textit{Some temnospondyl?}, \textit{Allosaurus}?, \textit{Dilophosaurus}?, \textit{Canis lupus?}, \textit{Crocuta crocuta}, \textit{Some shneakyshnake}, \textit{Homo sapiens}; Aquatic: \textit{Tiktaalik}, \textit{Some antiarchplacoderm}, Ichtyosauridae, \textit{Some metriorhynchidae?}, Mosasauridae, \textit{Basilosaurus}, \textit{Carcharodon carcharias}, \textit{Orcinus orca}.
\label{Timeline}
\end{figure}

\section*{Conclusion}
%TG: not sure where to put that in the conclusion but it'll be cool to mention that our scavenger scale can not only be used for the past but also for species hard to observe in the present (or even - if going wild - for predicted behavioral changes in the future!)
As is often the case in science, the present provides the key to the past.
The animals of today, while often different (sometimes radically so) to their ancestors, can be used to make informed comparisons to extinct species. 
We have used this technique to give insight into the drivers of scavenging across vertebrates through time.
In common with any other forager be they grazer, browser or predator, scavengers past and present have had to balance their energetic costs with the gains of food. 
The main factors we considered namely, encounter rate, handling time and prey availability can be used to create a scale of scavenging whereupon any species can be placed in order to establish the importance of carrion in it diet.
We hope this approach will be useful in the effort to explore this most understudied of feeding ecologies. 
% Add bits on climate change/dectection rate change, etc...
